Hidden Multiple Comparisons Increase Forensic Error Rates

### 2024-02-01 PNAS/index.Rnw
P(F_1) -> e

<<Accuracy, fig.cap="Probability of accurate decisions for $N$ comparisons for different error rates.", fig.width = 8, fig.height = 4>>=
r_vals <- tibble(r = c(.0005, 0.001, 0.005, .01, 0.05),
                 rlab = sprintf("P(F[1])==%0.05f", r))
res2 <- crossing(r = r_vals$r,
                 N = c(seq(1, 11, .01),seq(11.1, 109.9, .1), seq(110, 1100, 1))) %>%
  mutate(overall = (1 - r)^N) %>%
  left_join(r_vals)

>>>>

<<Accuracy, fig.cap="Probability of accurate decisions for $N$ comparisons for different error rates.", fig.width = 8, fig.height = 4>>=
r_vals <- tibble(r = c(.0005, 0.001, 0.005, .01, 0.05),
                 rlab = sprintf("e==%0.05f", r))
res2 <- crossing(r = r_vals$r,
                 N = c(seq(1, 11, .01),seq(11.1, 109.9, .1), seq(110, 1100, 1))) %>%
  mutate(overall = (1 - r)^N) %>%
  left_join(r_vals)
